Draft Documents

### 2022-11-06 src/draft.Rmd
descriptive analysis

```{r, message = F}
# required library
library(knitr)
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
```

@@

```{r}
ggplot(pov.reg,
       aes(x = year, y = pov, color = country.name)) +
  geom_point() +
  geom_smooth() +
  facet_grid(rows = vars(type))
```

There's a general steady, but distinct decline of poverty over time in each type of region.

>>>>

```{r, message = F}
# required library
library(knitr)
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(e1071)
library(moments)
```

@@

```{r}
ggplot(pov.reg %>% filter(country.code != "WLD"),
       aes(x = year, y = pov, color = country.name)) +
  geom_point() +
  geom_smooth() +
  facet_grid(rows = vars(type))
```

There's a general steady, but distinct decline of poverty over time in each type region of respective type. Latin America & Caribbean, Europe & Central Asia, Middle East & North Africa, and High Income group has a more gradual decline as they are not very poor to begin with.

Among the income groups, Low & Middle Income, Lower & Middle Income, and Upper Middle Income have quite similar in term of poverty indicator and slope over the year. While these values vary greatly among different geographical regions.

Let's see some important statistics

```{r}
stats <- poverty.headcount %>% 
  summarise(count = n(), skewness = skewness(pov), kurtosis = kurtosis(pov), std.deviation = sd(pov))

kable(stats)
```
